|

### 2022-07-28 manuscript.Rmd
clean up more figures

```{r plot-xy, fig.cap="Visualizing the relationship of two numerical variables with scatter plot.", fig.alt="Scatter plot representing the positive relationship between x and y variables.", echo=FALSE, fig.height=3}
# Prepare variables
x <- 1:5
y <- 1:5

@@

```{r tactile-producing-code, echo=TRUE, include=TRUE, cache=TRUE}
library(palmerpenguins)
library(tactileR)

brl_begin("figure/tactile-boxplot.pdf")
with(
  penguins,
  boxplot(body_mass_g ~ species)
)
brl_end()
```

```{r tactile-example, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, dependson="tactile-producing-code", fig.cap="Ready-to-print tactile graph in braille.", fig.alt="Boxplot showing the different body mass between penguins species"}
knitr::include_graphics("figure/tactile-boxplot.pdf")
```

>>>>

```{r plot-xy, fig.cap="Visualizing the relationship of two numerical variables with scatter plot.", fig.alt="Scatter plot representing the positive relationship between x and y variables.", echo=FALSE, fig.height=5}
# Prepare variables
x <- 1:5
y <- 1:5

@@

<!--added eval=FALSE to the chunk below because the output and messages were irrelevant-->

```{r tactile-producing-code, echo=TRUE, include=TRUE, cache=TRUE, eval=FALSE}

library(palmerpenguins)
library(tactileR)

brl_begin("tactile-boxplot.pdf")
with(penguins, boxplot(body_mass_g ~ species))
brl_end()
```

```{r echo=FALSE}
library(tactileR)
```

```{r tactile-example, echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, dependson="tactile-producing-code", fig.cap="Ready-to-print tactile graph in braille.", fig.alt="Boxplot showing the different body mass between penguins species", , fig.align = "center", out.height="50%"}
knitr::include_graphics("figure/tactile-boxplot.pdf")
```
